3D-printable micropipette

### 2015-01-26 publishing/plos_template.tex
added design and started validation in materials

% You may title this section "Methods" or "Models". 
% "Models" is not a valid title for PLoS ONE authors. However, PLoS ONE
% authors may use "Analysis" 
\section*{Materials and Methods}

>>>>

% You may title this section "Methods" or "Models". 
% "Models" is not a valid title for PLoS ONE authors. However, PLoS ONE
% authors may use "Analysis" 
\section*{Materials and Methods}
\subsection*{Design}
The device is designed to actuate a pipette to a set distance.
The pipette is plunger is actuated to three points, two fixed and one adjustable.
The fixed points are the dispensed point, when the plunger is all the way down, and the reset point, when the plunger is ready to withdraw fluid.
The adjustable point is the set point, which determines the volume of fluid that will be drawn into the pipette and dependes on the position of the screw.
The system is spring loaded towards the set point.
A springed notch, in the plunger shaft part, and a groove, in the body part, hold the plunger at the reset position where it can be released by pressing in the notch.
A 1 mL BD syringe twists to lock into the body part.
An additional printed part adapts standard micropipette tips to the luer fitting of the pipette.

Our printed pipette mimics commercial pipettes is design, function, and user operation, and is intuitive to use.

3D parts were designed in Blender and SolidWorks and printed by Fineline Protoypeing via selective laser sintering. 
Additional materials include a spring, a nut and bolt and two washers.

\subsection*{Validation}

The pipette was validated and compared to a commerical pipette. 
The pipette was tested to see if the set point would drift between during use for example small, incremental movements of the screw or other parts causing the pipetted volume to drift.
To test the pipette the same volume was pipetted 50 times without moveing or re-adjusting the set point. 
The printed pipette's accuracy and precicion was charaterized and compared to a commericial pipette.
